%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%    PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[scale=0.80]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%    NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Christopher} % Your first name
\familyname{Morgan} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Resume}
\address{3/11a Arcadia Rd, Epsom}{Auckland, New Zealand}
\mobile{+64 21 0224 2161}
\email{chris.j.r.morgan@gmail.com}
\homepage{github.com/drpotato} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
% \extrainfo{additional information}
% \photo[70pt][0.4pt]{picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
% \quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}
\makecvtitle% Print the CV title

\vspace{-1.5cm}

%----------------------------------------------------------------------------------------
%    WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Professional Experience}

\cventry{Nov 2014 --- Present}{Software Engineer Intern}{Hapara Inc.}{Auckland}
{}{Currently working in the Interact Team, building parts of a web application
    and peripheral products. Mainly developing in Python (AppEngine, Cloud
    Endpoints) and JavaScript (AngularJS). Researched possible new products and
    business opportunities.}

\cventry{Jul 2013 --- Nov 2014}{Full Stack Developer}{Young \& Shand}{Auckland}
{}{Developed cloud based applications (both frontend and backend) for clients,
    collaborating with colleagues with different skill sets. Administered
    AWS/Rackspace Linux servers, MySQL databases and deployment system.}

%----------------------------------------------------------------------------------------
%    EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2011 --- Present}{Bachelor of Engineering (Software)}{The University of
Auckland}{New Zealand}{}{}  % Arguments not required can be left empty

%----------------------------------------------------------------------------------------
%    PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{Projects}
\cventry{Ongoing}{Cost of Living Research}{Personal}{}{}{The goal is to create
    an interactive map of Auckland to determine the cost of living given a
    location of work or study. Currently building tools in Python to retrieve
    the needed information.}
\cventry{2015}{Scannp}{Personal}{}{}{iOS/Android app for scanning University of
    Auckland student IDs using Parse and Swift. Will be used by the Software
    Engineering Students Association for events and registration.}
\cventry{2014}{Interact}{Hapara Inc}{}{}{Refactored Interact Chrome extension
    to be more testable, secure and include increased metrics for usage and
    runtime errors.}
\cventry{2014}{Pysh}{University course in Operating Systems}{}{}{Python Shell.
    Incorporated piping, background jobs and history. Utilised lexical
    analysis, threading and introspection.}
\cventry{2014}{Filtr}{University course in Software Architecture}{}{}{Profanity
    filter API and consuming frontend client. Made API backend using Java
    Spring Framework, Hibernate and frontend using AngularJS.}
\cventry{2013}{Geckoboards}{Young \& Shand}{}{}{Built dashboards to pull in
    data from Dropbox, Facebook, Bitbucket, Google Analytics and Google AdWords
    to a dashboard for business development. Used Python, RabbitMQ and
    Raspberry Pis.}

%----------------------------------------------------------------------------------------
%    COMPETITION SECTION
%----------------------------------------------------------------------------------------

\section{Competitions}

\cventry{2014}{NZPC}{Team: Evolving Potato Pheonix}{7\textsuperscript{th} in
open tertiary bracket}{}{}
\cventry{2013}{IEEExtreme}{Team: Forkbomb}{1\textsuperscript{st} in New Zealand
and 14\textsuperscript{th} worldwide}{}{}

%----------------------------------------------------------------------------------------
%    INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}
\cvitem{}{In my spare time I enjoy playing card and board games, photography,
    reading comics, listening to vinyl records, making videogames and finding
    out interesting facts using Python. I was elected Vice President of the
    Software Engineering Students Association this year.}

\end{document}
